---
title: "HW2"
author: "Martha Walters"
date: "December 3, 2024"
output:
html_document:
df_print: paged
---


```{r setup}
# set up
library(tidyverse)
library(readxl)
library(testthat)
library(assertthat)
library(devtools)
#knitr::opts_chunk$set(include = FALSE)
```


# Exercise 1: Function call in R packages

```{r}
load_all("../hw2")
```

```{r, include = T, warning = F}
plot_cp(dat, est, iso_code = 4)
plot_cp(dat, est, iso_code = 4, CI = NA)
plot_cp(dat, est, iso_code = 404, CI = 80)
```

# Exercise 2: Add documentation 

Document the arguments and output of plot_cp. To do that, add a helpfile (.Rd file in subfolder man) using the approach from the class material "documenting an r package":

- add roxygen skeleton to the plot_cp function, fill in the details
- use the function document to generate the Rd file

In order to show the help file in the knitted Rmd, install the package Rd2md and use this code block:

```{r}
library(Rd2md)
Rd2markdown(rdfile = "man/plot_cp.Rd", outfile = "plot_cp.md")
```
# Plot mCPR data and estimates

## Description

Plot mCPR data and estimates

## Usage

```r
plot_cp(dat, est, iso_code, CI = 95)
```

## Arguments

* `dat`: tibble which contains mCPR observations. Columns: iso, year, cp
* `est`: tibble which contains mCPR estimates. Columns: Country or area, iso, Year, Median, U95, L95, U80, L80
* `iso_code`: country iso code
* `CI`: confidence intervals to be plotted. Options can be: 80, 95, or NA (no CI plotted)

## Value

ggplot object with mCPR observations and estimates over time

# Exercise 3: GitHub

https://github.com/waltersm16/hw2.git

